R Notebook

### 2019-07-02 ICS_Cleaning.Rmd
proportions calculations

>>>>

```{r create new combo variables from exported boolean phenotype}
CD4<-mutate(CD4,
      #These all follow the same format
       #IFNg is the new variable. it gets assign the row sum of all the columns that have a G in the name
       TbetCXCR3=  rowSums(CD4[,grep("t_._3_.", names(CD4))]),
       TbetCCR4=  rowSums(CD4[,grep("t_._._4", names(CD4))]),
       GATA3CXCR3=  rowSums(CD4[,grep("._g_3_.", names(CD4))]),
       GATA3CCR4=  rowSums(CD4[,grep("._g_._4", names(CD4))]),
       CXCR3.Tbetprop = TbetCXCR3/Tbet,
       CCR4.Tbetprop = TbetCCR4/Tbet,
       CXCR3.GATA3prop= GATA3CXCR3/GATA3,
       CCR4.GATA3prop= GATA3CCR4/GATA3
)

CD4_phenotype<-mutate(CD4_phenotype,
      #These all follow the same format
       #IFNg is the new variable. it gets assign the row sum of all the columns that have a G in the name
       TH1_TbetCXCR3=  rowSums(CD4_phenotype[,grep("TH1_t_._3_.", names(CD4_phenotype))]),
       TH1_TbetCCR4=  rowSums(CD4_phenotype[,grep("TH1_t_._._4", names(CD4_phenotype))]),
       TH1_GATA3CXCR3=  rowSums(CD4_phenotype[,grep("TH1_._g_3_.", names(CD4_phenotype))]),
       TH1_GATA3CCR4=  rowSums(CD4_phenotype[,grep("TH1_._g_._4", names(CD4_phenotype))]),
      TH2_TbetCXCR3=  rowSums(CD4_phenotype[,grep("TH2_t_._3_.", names(CD4_phenotype))]),
      TH2_TbetCCR4=  rowSums(CD4_phenotype[,grep("TH2_t_._._4", names(CD4_phenotype))]),
      TH2_GATA3CXCR3=  rowSums(CD4_phenotype[,grep("TH2_._g_3_.", names(CD4_phenotype))]),
      TH2_GATA3CCR4=  rowSums(CD4_phenotype[,grep("TH2_._g_._4", names(CD4_phenotype))]),

       TH1_CXCR3.Tbetprop = TH1_TbetCXCR3/TH1_Tbet,
       TH1_CCR4.Tbetprop = TH1_TbetCCR4/TH1_Tbet,
       TH1_CXCR3.GATA3prop= TH1_GATA3CXCR3/TH1_GATA3,
       TH1_CCR4.GATA3prop= TH1_GATA3CCR4/TH1_GATA3,

       TH2_CXCR3.Tbetprop = TH2_TbetCXCR3/TH2_Tbet,
       TH2_CCR4.Tbetprop = TH2_TbetCCR4/TH2_Tbet,
       TH2_CXCR3.GATA3prop= TH2_GATA3CXCR3/TH2_GATA3,
       TH2_CCR4.GATA3prop= TH2_GATA3CCR4/TH2_GATA3
)
